---
title: "Course_Project_1"
author: "bstan92"
date: "11/22/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Code for reading in the dataset and/or processing the data


```{r setup_data}

library(dplyr)

data <- read.csv("activity.csv")


```

## Histogram of the total number of steps taken each day


```{r hist1}
total_steps <- data %>% group_by(date) %>% summarise(tot_steps = sum(steps, na.rm = TRUE))
hist(total_steps$tot_steps)
```

## Mean and median number of steps taken each day

```{r mean_med}
mean_steps <- data %>% group_by(date) %>% summarise(mean = mean(steps, na.rm = TRUE))

median_steps <- data %>% group_by(date) %>% summarise(median = median(steps, na.rm = TRUE))
```

## Time series plot of the average number of steps taken

```{r time_series}
avg_steps_interval <- data %>% group_by(interval) %>% summarise(avg = mean(steps, na.rm = TRUE))

plot(avg_steps_interval$avg ~ avg_steps_interval$interval, type = "l")
```

## The 5-minute interval that, on average, contains the maximum number of steps

```{r max_int}
avg_steps_interval[avg_steps_interval$avg == max(avg_steps_interval$avg),]$interval
```

## Code to describe and show a strategy for imputing missing data

NAs will be populated with the average number of steps for that interval

```{r impute}
data <- left_join(data, avg_steps_interval, by = "interval")

data$steps_impute <- coalesce(as.numeric(data$steps), data$avg)
```

## Histogram of the total number of steps taken each day after missing values are imputed

```{r hist2}
total_steps <- data %>% group_by(date) %>% summarise(tot_steps = sum(steps_impute, na.rm = TRUE))

hist(total_steps$tot_steps)
```

## Panel plot comparing the average number of steps taken per 5-minute interval across weekdays and weekends

```{r panel}
data$day <- weekdays(as.Date(data$date))

weekend_avg <- data %>% filter(day == c('Saturday','Sunday')) %>% group_by(interval) %>% summarise(avg_steps = mean(steps_impute))
weekday_avg <- data %>% filter(day != c('Saturday','Sunday')) %>% group_by(interval) %>% summarise(avg_steps = mean(steps_impute))

par(mfrow=c(1,2))

plot(weekend_avg$avg_steps ~ weekend_avg$interval, type = "l")
plot(weekday_avg$avg_steps ~ weekday_avg$interval, type = "l")
```
